A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-25 4_method.tex
redo reduction/retreating figure

\begin{figure}
\centering
\setlength{\figwidth}{\columnwidth}
\begin{subfigure}{0.45\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_unreduced.pdf}
\caption{No reduction}
\end{subfigure}
\begin{subfigure}{0.45\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/method/polyline_reduction_reduced.pdf}
\caption{Reduction}
\end{subfigure}
\caption{
Reducing polyline toolpaths away from intersections in order to prevent overfill.
Toolpath locations in black, underfill in azure and overfill in orange.
Intersections result in overfill, so we remove parts of the toolpaths at intersections.
}
\label{polyline_reduction}
\end{figure}

>>>>

\begin{figure}
\centering
\setlength{\figwidth}{.35\columnwidth}
\begin{subfigure}{0.45\columnwidth}\centering
\includegraphics[width=\figwidth]{sources/method/polyline_reduction_before}
\caption{No reduction}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}\centering
\includegraphics[width=\figwidth]{sources/method/polyline_reduction_after}
\caption{Reduction}
\end{subfigure}
\caption{
Reducing polyline toolpaths away from intersections in order to prevent overfill.
Toolpath locations in black, underfill in azure and overfill in orange.
}
\label{polyline_reduction}
\end{figure}
